---
title: "Non-overlapping Block Bootstrap"
author: ""
date: "27 August 2018"
output: 
  html_notebook: 
    df_print: kable
    code_folding: hide
    highlight: tango
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
#######################
# Global Code Options #
#######################
knitr::opts_chunk$set(echo = TRUE, results = 'hide', tidy = TRUE,
                      cache = FALSE, prompt = FALSE,
                      comment = NA, message = FALSE, warning = FALSE)
#'
########################################
# Load Project Libraries and Functions #
########################################
k_path_project <<- rprojroot::find_rstudio_root_file()
source(file.path(k_path_project, "code", "scripts", "setup.R"))
```

## Why, How, What?

Block bootstrap procedure is the most widely used in a domain of time series. It maintains the time series dependency structure within a pseudo-sample.


In the non-overlapping block bootstrap, the variable of interest is split into non-overlapping blocks.

## Problem Setup

Assume a time series with:

* `time_horizon` number of minutes in the time series.

* `time_resolution` number of minutes per sample. 


```{r, out.width = "100%", dpi = 200, fig.height = 8}
# n_bs <- 2 # number of bootstrap samples
time_horizon <- 3 * 60 # length of time series [minutes]
time_resolution <- 10  # lenght of each sample [minutes]
n_instances <- time_horizon / time_resolution
```

