---
title: "Wide data"
subtitle: "Variable Significance and Variable Pruning"
author: ""
date: "05 September 2018"
output: 
  html_notebook: 
    df_print: kable
    highlight: tango
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
#######################
# Global Code Options #
#######################
knitr::opts_chunk$set(echo = TRUE, results = 'hide', tidy = FALSE,
                      cache = FALSE, prompt = FALSE,
                      comment = NA, message = FALSE, warning = FALSE)
#'
########################################
# Load Project Libraries and Functions #
########################################
k_path_project <<- rprojroot::find_rstudio_root_file()
source(file.path(k_path_project, "code", "scripts", "setup.R"))
```


A worked example

As an example, we give a regression problem with:
* 2 numeric inputs (one signal sigN, one noise, noiseN), and 
* 2 high-cardinality, with 100 levels, categoric inputs (one signal, sigC, and one noise, noiseC).

```{r generate_dataset, echo=TRUE, results='markup'}
set.seed(22451)
N <- 500
sigN <- rnorm(N)
noiseN <- rnorm(N)
Nlevels <- 100
zip <- paste0('z', format(1:Nlevels, justify="right"))
zip <- gsub(' ', '0', zip, fixed=TRUE)

zipval <- runif(Nlevels); names(zipval)=zip
sigC <- sample(zip, size=N, replace=TRUE)
noiseC <- sample(zip, size=N, replace=TRUE)

y <- sigN + zipval[sigC] + rnorm(N)
df <- data.frame(sN = sigN, nN = noiseN, sC = sigC, nC = noiseC, y = y)

dim(df)
head(df) %>% kableExtra::kable(format = "markdown")
```

Designing a treatment plan from this data gives us the following derived variable types (we ignore the catP and catD variable types)

```{r treatment_plan, echo=TRUE, results='markup'}
treatplan <- designTreatmentsN(df,
                               varlist = base::setdiff(colnames(df), "y"),
                               outcomename = "y",
                               verbose = FALSE)
names(treatplan)
# scoreFrame contains the significance of each variable
vtreat_sframe <- treatplan$scoreFrame
dim(vtreat_sframe)
kableExtra::kable(vtreat_sframe %>% arrange(varName),
                  format = "markdown", digits = 2)

vtreat_code <- vtreat_sframe$code
print(vtreat_code %>% unique())

# Ignore prevelances (catP) and conditional deviations (catD) variables
vars <- 
    vtreat_sframe %>% 
    dplyr::filter(!vtreat_code %in% c("catP", "catD")) %>%
    .$varName

vtreat_sframe %>% 
    dplyr::filter(varName %in% vars) %>% 
    dplyr::select(varName, sig, extraModelDegrees) %>%
    kableExtra::kable(format = "markdown")
```

Setting the pruning threshold to $p=\frac{1}{n_{var}}$
(in this case $p=$ `r round(1/length(vars),3)`), we accept:

* the signaling numeric variable sN, 
* the impact coding of the signaling categorical variable sC_catN, and 
* an indicator corresponding to one of sC’s levels.

All derived variables corresponding to the original noise variables are rejected

The function `vtreat::prepare` takes the argument pruneSig to pass in the desired pruning threshold.

```{r treatment_prepare, echo=TRUE, results='markup'}
pruneSig <- 1/length(vars)
dfTreat <- vtreat::prepare(treatplan, df, pruneSig = pruneSig,
                           varRestriction = vars)
head(dfTreat) %>% kableExtra::kable(format = "markdown")
```

```{r, out.width = "100%", dpi = 200, fig.height = 8}

```

